%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{

  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item\large
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeWorkSubheading}[6]{
  \vspace{-3pt}\item\large
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small #5} & \textit{\small #6}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item 
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge  \scshape Dmytro Moshkovskyi} \\ \vspace{5pt} 
    \small 561-859-8751 $|$ \href{mailto:x@x.com}{\underline{dm361167@ucf.edu}} $|$ 
    \href{https://linkedin.com/in/dmmosh}{\underline{linkedin.com/in/dmmosh}} $|$
    \href{https://github.com/dmmosh}{\underline{github.com/dmmosh}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeWorkSubheading
      {University of Central Florida}{Orlando, FL}
      {Bachelor of Science in Computer Science, \textbf{GPA 3.9}}{August 2023 -- May 2027}
      {Knight Hacks Member}{September 2023 -- Present}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {{\href{https://www.linkedin.com/posts/dmmosh_i-am-thrilled-to-announce-that-i-am-starting-activity-7346303516228894720-Kaab?utm_source=share&utm_medium=member_desktop&rcm=ACoAAD6UHAYBmUbVd8N5xFVrmRFWwILywSrvD6s}{\textbf{\underline{AI Intern}}}} }{July 2025 -- January 2026}
      {\href{https://yellow.ai/}{\underline{Yellow.AI}}}{Remote}
      \resumeItemListStart
        \resumeItem{Contributed as part of a collaborative team deploying AI voice and chat bots.}
        \resumeItem{Automated monitoring using \textbf{Python scripts} with the \textbf{Gemini API}, noted for saving \textbf{weeks} of conversation monitoring.}
        \resumeItem{Used {\href{https://www.cekura.ai/}{\underline{Cekura.AI}}} for \textbf{unit testing}, providing AI-driven testing benchmarks.}
         \resumeItem{Assisted in \textbf{prompt engineering}, writing complex logical rules for bots to follow.}
        \resumeItem{Assisted in a wide range of the production process such as development, debugging, testing, and analytics.}
        \resumeItem{Debugged the conversation logs, documenting and analyzing both client-side and server-side issues.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
         {{\href{https://www.linkedin.com/posts/dmmosh_knighthoot-knighthoot-is-a-real-time-interactive-activity-7394782454399647745-K_mf?utm_source=share&utm_medium=member_desktop&rcm=ACoAAD6UHAYBmUbVd8N5xFVrmRFWwILywSrvD6s}{\textbf{\underline{Knighthoot}}}} $|$ \emph{MERN Stack, Github, Project Management}}{October 2025 -- November 2fdshcki025}
          \resumeItemListStart
            \resumeItem{Was the \textbf{team lead of a group of 7}, coordinating a full-stack web and mobile platform.}
            \resumeItem{Worked with the team to develop a syncing pipeline between multiple clients and the server.}
            \resumeItem{Managed a \textbf{Ubuntu} web server on DigitalOcean with a \textbf{MongoDB} database and \textbf{HTTPS port forwarding}.}
            \resumeItem{Earned a grade of \textbf{100/100} and received appraise from the professor for going above the project expectations.}
          \resumeItemListEnd
      \resumeProjectHeading
          {{\href{https://www.linkedin.com/posts/dmmosh_i-am-building-my-own-search-engine-my-activity-7410459679161561088-fjuE?utm_source=share&utm_medium=member_desktop&rcm=ACoAAD6UHAYBmUbVd8N5xFVrmRFWwILywSrvD6s}{\textbf{\underline{Lightning Search}}}}  $|$ \emph{Python, C++, PyTorch, LibTorch, Sockets}}{December 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack search engine built from scratch with C++ sockets, utilizing \href{https://exa.ai/}{\underline{Exa Search}}.}
            \resumeItem{Trained a large word autocomplete neural network model and implemented in the server.}  
            \resumeItem{Loaded the model in the server through LibTorch.}
          \resumeItemListEnd
          \resumeProjectHeading
          {{\href{https://www.linkedin.com/posts/dmmosh_fspot-pre-alpha-build-what-is-it-a-fast-activity-7194348197018779648-wZon?utm_source=share&utm_medium=member_desktop&rcm=ACoAAD6UHAYBmUbVd8N5xFVrmRFWwILywSrvD6s}{\textbf{\underline{FSPOT}}}}  $|$ \emph{C++, HTTP Requests, Optimization}}{August 2024 -- October 2024}
          \resumeItemListStart
            \resumeItem{Developed a full-feature Spotify TUI Client with integration to the \href{https://github.com/librespot-org/librespot}{\underline{Librespot receiver}}.}
            \resumeItem{Optimized the program to use \textbf{30mb of RAM} as compared to Spotify's \textbf{600mb}, reducing memory footprint of listening to music by \textbf{2000\%}.}
          \resumeItemListEnd
           \resumeProjectHeading
         {{\href{https://github.com/mirthless7/onePieceSummarizer}{\textbf{\underline{One Piece Summarizer}}}} $|$ \emph{Python, Machine Learning}}{October 2023}
          \resumeItemListStart
            \resumeItem{Coordinated \textbf{a group of 3} to deploying a machine learning model.}
            \resumeItem{Worked under tight time constraints, finishing the project in \textbf{just 36 hours}.}
            \resumeItem{Led the team to winning the 2023 Knight Hacks Hackathon Frying Pan award.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{ \item{
    \textbf{Languages}{: Python, C/C++, SQL (MongoDB), JavaScript, Bash} \\
     \vspace{3pt} \textbf{Libraries}{: PyTorch, LibTorch, Boost Library, Pandas, NumPy, Matplotlib, JSON} \\
     \vspace{3pt} \textbf{Frameworks}{: React, Node.js, Express.js} \\
     \vspace{3pt}\textbf{Developer Tools}{: Git, Github, VS Code, CMake, OpenSSL} \\
    } }
 \end{itemize}


%-------------------------------------------
\end{document}

